PubCrawl: A Publication Search Engine

### 2012-05-17 report/paper.tex
Include the PageRank equation to explain the parameters we set

PageRank is a well-known algorithm for estimating the importance of a web page
as a function of the number of incoming links \cite{brin98, page99}. It is
plausible to extend the algorithm by analogy to academic papers and citations.
We use the iterative algorithm as described but tune the parameters to improve
the quality of the results for the ACM data set.

We set the score source $E$ to a uniform vector with each coordinate equal to
$0.1$. This setting minimizes the PageRank each paper gets for free while still
allowing the algorithm to converge. We set the damping factor $d$ to the
suggested value of $0.85$. This setting reduces the number of iterations needed
to converge by reducing the amount of PageRank contributed in subsequent
iterations.

>>>>

PageRank is a well-known algorithm for estimating the importance of a web page
as a function of the number of incoming links \cite{brin98, page99}. It is
plausible to extend the algorithm by analogy to academic papers and citations.
We use the iterative algorithm as described but tune the parameters to improve
the quality of the results for the ACM data set. The update rule is:

\begin{equation}
R(p)= n\left(\frac{1 - d}{N} + d\left(\sum_{c \in C}
\frac{R(c)}{D(c)}+E(p)\right)\right)
\end{equation}

where $R(\cdot)$ is the PageRank of a node, $D(\cdot)$ is the outdegree of a
node, $E(\cdot)$ is the score source of a node (needed to converge with
cycles), $d$ is the damping factor, and $n$ is the normalizing factor.

We set $E$ to a uniform vector with each coordinate equal to $0.1$. This
setting minimizes the PageRank each paper gets for free while still allowing
the algorithm to converge. We set $d$ to the suggested value of $0.85$. This
setting reduces the number of iterations needed to converge by reducing the
amount of PageRank contributed in subsequent iterations.
